General exp analysis -- 4/18/2018

### 2018-04-30 resistingrhythm/analysis/paper_figures.Rmd
Update data for figs

```{r, message=FALSE}
# -----------------------------------------------------------------------
# 16: Burst E, with H
exp_code <- 16
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(0, 1)

results16 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

@@

    results16 <- rbind(results16, df)
  }
}

results16 %>%
  filter(rate_k > 0) -> results15

@@

# -----------------------------------------------------------------------
# 30: Burst I, with H
exp_code <- 30
osc_codes <- c(100, 101, 102, 103, 104, 105, 110, 115, 120, 125, 130, 135, 140, 145, 150, 155, 160)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(0, 1)

results30 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

@@

    results30 <- rbind(results30, df)
  }
}

results30 %>%
  filter(rate_k > 0) -> results30

@@

# Var
results16 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results16 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(mse_var), SD=sd(mse_var)) -> tmp2

@@

# -
# Rate
results16 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results16 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k - rate_ref), SD=sd(rate_k - rate_ref)) -> tmp2

@@

tmp4 <- results16
tmp4$osc_mode <- rep("Burst", nrow(results16))

@@

```{r, fig.width=2.4, fig.height=1.7}
# --------------------------------------------------------
# Burst
results16 %>% 
  filter(osc_rate >= 0 & osc_rate <= 0.5) %>% 
  group_by(osc_rate) %>% 
  summarise(M_var=mean(mse_var), 
         SD_var=sd(mse_var),
         M_error=mean(mse_error)/1e3,
         SD_error=sd(mse_error)/1e3) -> tmp1

@@

# Var
results30 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results30 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(mse_var), SD=sd(mse_var)) -> tmp2

@@

# -
# Rate
results30 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results30 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k - rate_ref), SD=sd(rate_k - rate_ref)) -> tmp2

@@

tmp4 <- results30
tmp4$osc_mode <- rep("Burst", nrow(results30))

@@

# Figure 4. Variable Calcium targets and sustained E

@@

p5 <- nullGrob()
p6 <- textGrob("Excitatory modulation")

>>>>

```{r, message=FALSE}
# -----------------------------------------------------------------------
# 16: Burst E, with H
exp_code <- 31
osc_codes <- c(500, 501, 502, 503, 504, 505, 510, 515, 520, 525, 530, 535, 540, 545, 550, 555, 560)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(0, 1)

results31 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

@@

    results31 <- rbind(results31, df)
  }
}

results31 %>%
  filter(rate_k > 0) -> results15

@@

# -----------------------------------------------------------------------
# 30: Burst I, with H
exp_code <- 32
osc_codes <- c(500, 501, 502, 503, 504, 505, 510, 515, 520, 525, 530, 535, 540, 545, 550, 555, 560)
osc_rates <- c(0, 0.1, 0.2, 0.3, 0.4, 0.5, 1.0, 1.5, 2.0, 2.5, 3.0, 3.5, 4.0, 4.5, 5.0, 5.5, 6.0)
stim_codes <- c(0, 1)

results32 <- NULL
for(i in 1:length(osc_codes)){
  for(s_c in stim_codes){
    o_c <- osc_codes[i]
    o_r <- osc_rates[i]

@@

    results32 <- rbind(results32, df)
  }
}

results32 %>%
  filter(rate_k > 0) -> results32

@@

# Var
results31 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results31 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(mse_var), SD=sd(mse_var)) -> tmp2

@@

# -
# Rate
results31 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results31 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k - rate_ref), SD=sd(rate_k - rate_ref)) -> tmp2

@@

tmp4 <- results31
tmp4$osc_mode <- rep("Burst", nrow(results31))

@@

```{r, fig.width=2.4, fig.height=1.7}
# --------------------------------------------------------
# Burst
results31 %>% 
  filter(osc_rate >= 0 & osc_rate <= 0.5) %>% 
  group_by(osc_rate) %>% 
  summarise(M_var=mean(mse_var), 
         SD_var=sd(mse_var),
         M_error=mean(mse_error)/1e3,
         SD_error=sd(mse_error)/1e3) -> tmp1

@@

# Var
results32 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results32 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(mse_var), SD=sd(mse_var)) -> tmp2

@@

# -
# Rate
results32 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) -> tmp1

results32 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  group_by(osc_rate) %>% 
  mutate(M=mean(rate_k - rate_ref), SD=sd(rate_k - rate_ref)) -> tmp2

@@

tmp4 <- results32
tmp4$osc_mode <- rep("Burst", nrow(results32))

@@

# Figure 4. Calcium targets

@@

p5 <- nullGrob()
p6 <- textGrob("Calcium level")
